%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[20pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Dr. Balakrishna}{Soorali Ganeshamurthy}
\address{Schwilkenhofstr 79B, 70439, Stuttgart, Germany.}
\mobile{+49 (0) 176-3096-2464} 
%%% Social
\email{balakrishnasg@daimler.com}
\linkedin{https://www.linkedin.com/in/balakrishnasg/}
%%% Optionals
\position{Data Scientist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {Herr Dr. Joachim Herbst}
  {Crowd Functions \& Technology Management ( RD/AFC ) }
\letterdate{\today}
\lettertitle{Subject: Job Application Data Scientist for Automated Driving - Crowd Data & Analytics  \vspace{1 cm}}
\vspace{1 cm}
\letteropening{Dear Dr. Joachim Herbst,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Dr. Balakrishna  Soorali Ganeshamurthy~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}

With this application I will like to express my strong interest in the position \textbf{Data Scientist (206966)}. Currently, I am working as a Data Scientist in Daimler Financial Services Stuttgart. My professional experience includes crafting algorithms and making use of machine learning to mine and make sense of data, and then using data visualization to present to decision makers. I have gained a quite good amount of IT skills that are necessary for a Data Scientist. Two years of experience in Daimler in a similar role with my passion for data, I think my profile suits well to this role.

\par Over the course of my career, I have worked with various use cases such as customer retention, collection optimization, and Lead Conversions, using advanced machine learning methods. Along with this, I have gained experience in text analysis, reinforcement learning and data mining methods. I have good programming experience using R, JAVA, and Python.
\par Having worked with data and mathematical modeling, I am expanding my skill set to include machine learning methods in my repertoire. I have looked at various datasets with state of the art algorithms and methods to improve prediction accuracy and processing speeds in Kaggle (community of data scientists and machine learners).  I am driven by challenging problems solving which require a multidisciplinary approach.
\par I would be happy to have an opportunity to discuss further my application and the role in detail.  Thank you for taking the time to consider my application. Looking forward to hearing from you.
\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
